---
title: "pre_diat"
author: "Mari Rivera"
date: "September 23, 2019"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r diatoms preprocessing}

library(here)
library(tidyverse)
library(dplyr)
library(tidyr)
library(analogue)
library(plotly)

####Possible  Caloneis biconstrictoides (LevkovWilliams2014)
#great http://symbiont.ansp.org/dntf/gallery.php?g=Caloneis&r=A-C

source('C:/Users/Maria Jose Rivera/OneDrive - James Cook University/Australia renamed/Sanamere/Thesis sections/PhD/preprocessing/pre_age_model.R')


diatoms_counts<-read.csv(here("experiments", "exp_diatoms","data", "Counts_diatoms_08_08_19.csv"))

diatoms_photo<-read.csv(here("experiments", "exp_diatoms","data", "Photos_silica.csv"))

###Concentration of diatoms
conc<-read.csv("C:/Users/Maria Jose Rivera/OneDrive - James Cook University/Australia renamed/Sanamere/Diatoms spicules/Concentration diatoms.csv")

diatoms_counts$Species2 <- paste(diatoms_counts$Genus,diatoms_counts$Species)
#phy_2$final_morphotype <- paste(phy_2$Morphotype,phy_2$Morphotype_b)
diatoms_counts$final_morphotype <- paste(diatoms_counts$Morphotype,diatoms_counts$Morphotype_b)

#Merging counts and concentration
diat_merge<-merge(diatoms_counts,conc,by="Identifier")
#diat_merge$Species2[diat_merge$Species2 == "Caloneis 999"] <- "Caloneis"
diat_merge$Identifier[diat_merge$Identifier == 0] <- 26

diat_merge2<-diat_merge%>%
     select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transects)%>%
        filter(Type=='Diatom')%>% 
        group_by(Identifier)%>%
        mutate(Corrected_counts=Counts/Total_sediment_analysed_g)%>%
        #mutate(Corrected_counts2=Counts/sum(Total_sediment_analysed_g))%>%
        mutate(countT= sum(Corrected_counts),countT2=sum(Counts)) %>%
       mutate(per=paste0(round(100*Corrected_counts/countT,2)))%>%
        mutate(d_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
        filter(Species2!="Caloneis 999")




#        mutate(corr_trans= countT2/Number_of_transects)%>%
#        filter(countT2 > 0)%>%
#       mutate(per2=paste0(round(100*Counts/countT2,2)))
        
#conc_all<-ggplot(diat_merge2,aes(x=Identifier,y=d_g_wet_sed))+geom_point()

#ggplotly(conc_all)

diat_merge3<-diat_merge%>%
        select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transects)%>%
        filter(Type=='Diatom')%>% 
            group_by(Identifier)%>%
        mutate(countT2=sum(Counts)) %>%
        mutate(per=paste0(round(100*Counts/countT2,2)))%>%
        mutate(d_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
        filter(countT2 > 0)%>%
        filter(Species2!="Caloneis 999")


diat_merge_age<-left_join(diat_merge3,agedepth2)

age<-ggplot(diat_merge_age,aes(y=median,(x=countT2/Number_of_transects)))+geom_point()  + ggtitle("")+xlab(")")+ylab("Age (cal yr BP)")+theme_bw() + theme(axis.text.x=element_text(size=12),axis.title.x=element_text(size=12,face="bold"),axis.title.y = element_text(size=12,face="bold"))

ggplotly(age)

diat_merge4<- diat_merge3%>%
       spread(Species2, per) 

diat_merge_pr<-diat_merge3%>%
        select(Identifier,Species2,Counts)%>%
        filter(Identifier!=132)%>%
       spread(Species2, Counts) %>%
        select(-2,-3)
        #select(Identifier,11:29)

diat_merge20<-select(diat_merge4,Identifier,11:29)

#diat_merge5<- aggregate(x=diat_merge4[,2:20], by=list(Identifier=diat_merge4$Identifier), min, na.rm = TRUE)
diat_merge11<- aggregate(x=diat_merge20[,2:20], by=list(Identifier=diat_merge4$Identifier), min, na.rm = TRUE)

diat_new<-left_join(diat_merge11,agedepth2)

#diat_new2<-select(diat_new,-(3:4))

diat_merge10<- aggregate(x=diat_new[,2:21], by=list(median=diat_new$median), min, na.rm = TRUE)

###Need to merge with new dates and model them with 0.5 cm resolution 

#str(diat_c2)

#diat_merge5[, c(1:20)] <- sapply(diat_merge5[, c(1:20)], as.numeric)

#diat_merge5[is.na(diat_merge5)] <- 0

#str(diat_c2)

      
#BAR_merge <- Stratiplot(Identifier ~ . , data= diat_merge5, type = c("h","g","l"), sort = "wa")
#BAR2_merge <- Stratiplot(Identifier ~ . , data= chooseTaxa(diat_merge5, max.abun = 5, n.occ = 1),
#                   type = c("h","g"), sort = "wa")


###########
diat_merge10[, c(1:20)] <- sapply(diat_merge10[, c(1:20)], as.numeric)

diat_merge10[is.na(diat_merge10)] <- 0

#diat_merge10<-diat_merge10[,-(1)]
diat_merge10<-diat_merge10[,-(21)]

      
#BAR_merge2 <- Stratiplot(median ~ . , data= diat_merge10, type = c("h","g","l"), sort = "wa")

diat_merge_16<-select(diat_merge10,-1)


diat_merge11<-select(diat_merge_pr,2:20)
diat_merge111<-select(diat_merge10,2:19)


diat_merge12<-as.data.frame(diat_merge11)
diat_merge12[is.na(diat_merge12)] <- 0
diat_merge13<-select(diat_merge12,-1)

#diat_merge12<-diat_merge11%>%
       # group_by(Identifier)
####
diat_merge14 <- scale(diat_merge13)
diat_merge144 <- scale(diat_merge111)
diat_merge15<- diat_merge14*diat_merge14
        

#diat_merge11<-select(diat_merge_pr,2:20)

#diat_merge_pr[is.na(diat_merge_pr)] <- 0
#diat_merge11 <- scale(diat_merge_pr)
#diat_merge11<- diat_merge11*diat_merge11
#diat_merge11<-as.data.frame(diat_merge11)
#diat_merge12<-select(diat_merge11,-1)
#diat_merge_pr<-select(diat_merge_pr,-1)

#diat_merge12<-diat_merge11%>%
 #       group_by(Identifier)
        


#diat_merge11<-select(diat_merge11,-1)
?prcurve

prcurve_diat<-prcurve(diat_merge111,method='ca',trace = TRUE,plotit = TRUE,vary = TRUE,penalty=1.4)
varExpl(prcurve_diat)
# Extract pricipal curve scores
scrs<-scores(prcurve_diat)
# Plot curve vs. Age
plot(scrs~diat_merge10$median, type="l")

#not sure
fit <- fitted(prcurve_diat) ## locations on curve
abun <- fitted(prcurve_diat, type = "smooths") ## fitted response



dissim<- vegdist(diat_merge15, method="bray")
#dissimilarity matrix computation

clust <- chclust(dissim, method="coniss")
?chclust
# Ball and Stick
groups<- bstick(clust,ng=5) #determine the appropriate number of significant clusters
ngroups<- groups$nGroups[which(groups$dispersion <= groups$bstick)]
ngroups<- ngroups[2]
cc<- cutree(clust, k = ngroups)
?bstick
?strat.plot
# STRAT plot
par(oma=c(2,1,1,1.2))
strat.plot(diat_merge_16, yvar=diat_merge10$median, clust=clust, y.rev=TRUE, cex.axis=0.6, cex.yaxis=0.8, cex.ylabel=0.8, cex.lab=0.6, ylab="cal BP (yr)", col.line="black", col.bar="black", las=3, mgp=c(3,1,0))
# check that strat plot is ok
#?par
x<-strat.plot(diat_merge_16, yvar=diat_merge10$median, clust=clust, y.rev=TRUE, cex.axis=0.6, cex.yaxis=0.8, cex.ylabel=0.8, cex.lab=0.6, ylab="cal BP (yr)",col.line="black", col.bar="black", las=3, mgp=c(3,1,0))

z<-as.matrix(1:ngroups)

addClustZone(x, clust, nZone=ngroups, col=rainbow(length(z))[rank(z)])
c <- cutree(clust, k=ngroups)
data$clust <- c
  
title(main=strat_title, cex.main=2)
?addClustZone

?gam
pca_diat <- prcomp(diat_merge_16, center=T, scale.=T)

?strat.plot

pca1_diat<-as.data.frame(pca_diat$x)

plot(pca1_diat$PC1~diat_merge10$median,type="l")


#pca22<-merge(pca1,prcurve_ITRAX,by="row.names")


library(FactoMineR)
library(factoextra)


?PCA
res.pca_diat <- PCA(diat_merge_16, graph = FALSE,scale.unit = TRUE)
dimdesc(res.pca_diat,axes=1)

plot(res.pca_diat, choix = 'varcor')

res.pca_diat$contrib

res <- PCA(diat_merge_16, scale.unit = FALSE, graph = FALSE)
loadings<-sweep(res$var$coord,2,sqrt(res$eig[1:5,1]),FUN="/")
print(loadings)

#Plot factormine package

eig.val <- get_eigenvalue(res.pca_diat)
eig.val

fviz_eig(res.pca_diat, addlabels = TRUE, ylim = c(0, 50))

#Scores with Factormine. Similar to x (in prcomp package). 

res.pca_diat$ind$coord

#Contributions of variables to PC1

fviz_contrib(res.pca_diat, choice='var', axes=1, top=26)

#Contributions of variables to PC2

fviz_contrib(res.pca, choice='var', axes=2, top=26)




#cpa_diat<-select(diat_merge10,16)

#cpa<-bcp(cpa_diat)

#cpaa<-sqrt(cpa_diat)
#cpaa<-as_vector(cpaa)

#library(bcp)
#library(forecast)
#library(quantreg)
#library(changepoint)
#bcp.diat<-bcp(cpaa,w0=0.2,p0=0.2,burnin=1000,mcmc=10000,return.mcmc = TRUE)

#spma<-ma(cpaa,10);spor.ma<-spma[which(spma>0)]
#depth.ma<-diat_merge10$median[which(spma>0)]
#plot(spma)
#plot(depth.ma,spor.ma,type="b")
#plot(bcp.diat)




BAR2_merge2 <- Stratiplot(median~ . , data= chooseTaxa(diat_merge10, max.abun = 5, n.occ = 1),
                   type = c("h","g"), sort = "wa",xlab="Relative percentage (%)",ylab="Age (cal yr BP)")


BAR2_merge3 <- Stratiplot(median~ . , data= chooseTaxa(diat_merge10, max.abun = 2, n.occ = 1),
                   type = c("h","g"), sort = "wa",xlab="Relative percentage (%)",ylab="Age (cal yr BP)")

?Stratiplot
#Leave surface samples out for concentration calcs
#con_diat_2<-filter(diat_new2,Identifier >0.1)

#con_diat<-ggplot(con_diat_2,aes(x=con_diat_2$Identifier,(y=sqrt(d_g_wet_sed))))+geom_point() + xlab("age")+ ylab("concentration")+ theme_bw()

#print(con_diat)


#Concentration over time

con_diat_1<-diat_merge3%>%
        merge(agedepth2)%>%
        filter(Identifier >0.1)%>%
        select(Depth,median,d_g_wet_sed)%>%
        filter(median>120)

con_diat_to_merge<-diat_merge3%>%
        merge(agedepth2)%>%
        select(Depth,median,d_g_wet_sed)%>%
        group_by(Depth)%>%
        unique()

con_diat_2<-ggplot(con_diat_1,aes(y=median,(x=sqrt(d_g_wet_sed))))+geom_point() +  scale_y_reverse(breaks = seq(0, 32500, by = 5000)) + scale_x_continuous(limits=c(0, 600), breaks=c(0,200,400,600)) + ggtitle("")+xlab("Sqrt of Concentration (diat/g)")+ylab("Age (cal yr BP)")+theme_bw() + theme(axis.text.x=element_text(size=12),axis.title.x=element_text(size=12,face="bold"),axis.title.y = element_text(size=12,face="bold"))


plot_conc <- con_diat_1 %>%
        select(Depth, d_g_wet_sed) %>%
        na.omit() %>%
        ggplot() +
        geom_point(aes(x = sqrt(d_g_wet_sed), y = Depth), size = 1, alpha = 0.75) + geom_path(aes(x = sqrt(d_g_wet_sed), y = Depth), size = 1, alpha = 0.75)+
        xlab("Diatom concentration (sqrt)") +
        theme_minimal() +
        scale_y_reverse(breaks = seq(0, 172.2, by = 25))+
        theme(axis.title.x=element_text(size=16),
              axis.title.y = element_blank(),
              axis.text.y = element_blank())

plot_conc

ggplotly(con_diat_2)

spi_2<-diat_merge%>%
        select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transects)%>%
        filter(Type=='Spicule')%>% 
            group_by(Identifier)%>%
        mutate(countT2=sum(Counts)) %>%
        mutate(per=paste0(round(100*Counts/countT2,2)))%>%
        mutate(spi_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
        filter(countT2 > 0)

spi_222<-left_join(spi_2,agedepth2)

spi_333 <- ggplot(spi_222,aes(y=median,(x=sqrt(spi_g_wet_sed))))+geom_point() +  scale_y_reverse(breaks = seq(0, 33000, by = 5000))  + ggtitle("")+xlab("Sqrt of Concentration (diat/g)")+ylab("Age (cal yr BP)")+theme_bw() + theme(axis.text.x=element_text(size=12),axis.title.x=element_text(size=12,face="bold"),axis.title.y = element_text(size=12,face="bold"))

spi_333
ggplotly(spi_333)
summary(spi_222$spi_g_wet_sed)

ggplotly(d501)
spi_diat<-merge(con_diat_to_merge,spi_222,all=TRUE)%>%
        filter(Identifier>0.1)%>%
        select(d_g_wet_sed,spi_g_wet_sed,median)%>%
        drop_na()
age_2<-ggplot(spi_diat,aes(y=median,(x=sqrt(spi_g_wet_sed)))) +geom_point()+ ggtitle("")+xlab(")")+ylab("Age (cal yr BP)")+theme_bw()

age_2

age_3<-ggplot(spi_diat,aes(y=median,(x=sqrt(d_g_wet_sed))))+geom_point()  + ggtitle("")+xlab(")")+ylab("Age (cal yr BP)")+theme_bw()

age_3
ggplotly(age_2)


cor(spi_diat)
```

#main reference: mcz064_suppl Nomenclature 2.0, Neumann et al.
##Should include depths with low counts????
#Should reorganize to include the corrected version with concentration
#Stratplot with corrected counts by conc is ready and also diat, phy and sp conc
#Should group the counts by gssc/poaceae, woody (Dicotyle), 3D=blocky, mono vs dico difference?

morphotype<-c("Globular echinate","Elongate echinate", "Elongate sinuous", "Globular psilate", "Hair", "Tracheids", "Blocky faceted", "Blocky polyhedron","Globular decorated","Parallelepiped blocky","Cyperaceae","Elongate psilate","Elongate facetated")

plant_group<-c("Woody dicotyledons (Arecaceae?)","Non_diagnostic","Non_diagnostic","Non_diagnostic", "Non_diagnostic","Non_diagnostic","Woody Dicotyledons", "Woody Dicotyledons","Woody Dicotyledons","Woody Dicotyledons","Woody Dicotyledons","Grasses and sedges","Grasses and sedges")

df<-data.frame(morphotype,plant_group)

df
#next step is to count "wood" or globular granulate phytoliths
#check thesis to see what it means to have the different types ??? of phytoliths





##include concentrations of biogenic silica. No phytoliths peaty layer? why? accumulation is different? different vegetation - groups that produce more or less phytoliths

######NEED TO check, cunt and include phytoliths <20 in all samples!!! Maybe SPIC species

#par(mfrow=c(1,1))


#####92???? COrrect 93 for counts and transects
#CHeck superficial, 2H or other, check fractions <20 um, 28 (frustulia vs Brachisyra), do maybe 30 and 55

#New column putting together Genus and species




#diat_sp<-diatoms_counts %>%
       # filter(Type=='Diatom')%>% 
            #roup_by(Species2)

#photos<-anti_join(diat_sp,diatoms_photo)

#str(diat_sp$Species2)
#diat_sp$Species2<-as.factor(diat_sp$Species2)
#str(diatoms_photo$Species2)
#character to factor

#####Correcting by volume and amount of sediment used


#diatoms_counts2<-read.csv("C:/Users/Maria Jose Rivera/OneDrive - James Cook University/Australia renamed/Sanamere/Diatoms spicules/Counts_diatoms_08_08_19.csv")

#diatoms_counts2$Species2 <- paste(diatoms_counts2$Genus,diatoms_counts2$Species)






#diat_merge22<-diat_merge%>%
        #select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transec#ts)%>%
 #       filter(Type=='Diatom')%>% 
  #      group_by(Identifier)%>%
   #      mutate(Corrected_counts=Counts/Total_sediment_analysed_g)%>%
    #       mutate(countT= sum(Corrected_counts),countT2=sum(Counts)) %>%
     #   mutate(per=paste0(round(100*Corrected_counts/countT,2)))%>%
      #  mutate(d_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
       # filter(d_g_wet_sed < 300000)

        
#plot(diat_merge22$Identifier,diat_merge22$d_g_wet_sed)
#diat_333 <- ggplot(diat_merge2, aes(x=Identifier,y=d_g_wet_sed))+geom_point() 
#diat_333



#con_diat3<-ggplot(diat_new2,aes(x=diat_new2$Identifier,(y=sqrt(d_g_wet_sed))))+geom_point() + xlab("age")+ ylab("concentration")+ theme_bw()

#print(con_diat3)
######################################spicules

diat_merge<-merge(diatoms_counts,conc,by="Identifier")


#spi_2<-diat_merge%>%
 #     select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transects)%>%
  #      filter(Type=='Spicule')%>% 
   #     group_by(Identifier)%>%
    #    mutate(Corrected_counts=Counts/Total_sediment_analysed_g)%>%
     #   mutate(countT= sum(Corrected_counts),countT2=sum(Counts)) %>%
      #  mutate(per=paste0(round(100*Corrected_counts/countT,2)))%>%
       # mutate(d_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
        #mutate(corr_trans= countT2/Number_of_transects)%>%
        #filter(countT2 > 0)
        

spi_2<-diat_merge%>%
        select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transects)%>%
        filter(Type=='Spicule')%>% 
            group_by(Identifier)%>%
        mutate(countT2=sum(Counts)) %>%
        mutate(per=paste0(round(100*Counts/countT2,2)))%>%
        mutate(spi_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
        filter(countT2 > 0)

#diat_merge22<-diat_merge%>%
        #select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transec#ts)%>%
 #       filter(Type=='Diatom')%>% 
  #      group_by(Identifier)%>%
   #      mutate(Corrected_counts=Counts/Total_sediment_analysed_g)%>%
    #       mutate(countT= sum(Corrected_counts),countT2=sum(Counts)) %>%
     #   mutate(per=paste0(round(100*Corrected_counts/countT,2)))%>%
      #  mutate(d_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
       # filter(d_g_wet_sed < 300000)

        
#plot(diat_merge22$Identifier,diat_merge22$d_g_wet_sed)
#diat_333 <- ggplot(diat_merge2, aes(x=Identifier,y=d_g_wet_sed))+geom_point() 
#diat_333
#spi_3<-spi_2%>%
 #       filter(Type=='Spicule')%>% 
  #          group_by(Identifier)%>%
   #     mutate(countT= sum(Corrected_counts),countT2=sum(Counts)) %>%
    #    mutate(per=paste0(round(100*Corrected_counts/countT,2)))%>%
     #   mutate(spi_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
      #  filter(countT2 > 0)

spi_222<-left_join(spi_2,agedepth)

spi_333 <- ggplot(spi_222,aes(y=median,(x=sqrt(spi_g_wet_sed))))+geom_point() +  scale_y_reverse(breaks = seq(0, 32500, by = 5000))  + ggtitle("")+xlab("Sqrt of Concentration (diat/g)")+ylab("Age (cal yr BP)")+theme_bw() + theme(axis.text.x=element_text(size=12),axis.title.x=element_text(size=12,face="bold"),axis.title.y = element_text(size=12,face="bold"))
 
spi_333

#############################
#Phytoliths
#phy_2<-diat_merge%>%
 #     #select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transects)%>%
  #      filter(Type=='Phytoliths')%>% 
   #     group_by(Identifier)%>%
    #    mutate(Corrected_counts=Counts/Total_sediment_analysed_g)%>%
     #   mutate(countT= sum(Corrected_counts),countT2=sum(Counts)) %>%
     #   mutate(per=paste0(round(100*Corrected_counts/countT,2)))%>%
     #   mutate(phy_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
     #   mutate(corr_trans= countT2/Number_of_transects)%>%
      #  filter(countT2 > 0)


phy_2<-diat_merge%>%
        select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transects,final_morphotype)%>%
        filter(Type=='Phytoliths')%>% 
            group_by(Identifier)%>%
        mutate(countT2=sum(Counts)) %>%
        mutate(Corrected_counts=Counts/Total_sediment_analysed_g)%>%
        mutate(per=paste0(round(100*Counts/countT2,2)))%>%
        mutate(phy_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
        filter(countT2 > 0)

#Graph by morphotype
phy_222<-left_join(phy_2,agedepth)
phy_223<-ggplot(phy_222, aes(x=phy_222$median,y=Corrected_counts, color=final_morphotype))+geom_point()+ scale_color_hue(h = c(80, 1000))

phy_223
#str(phy_222)
phy_222$final_morphotype<-as.factor(phy_222$final_morphotype)


#Concentration graph
phy_444<-ggplot(phy_222, aes(y=median,(x=sqrt(phy_g_wet_sed))))+geom_point() +  scale_y_reverse(breaks = seq(0, 32500, by = 5000))  + ggtitle("")+xlab("Sqrt of Concentration (diat/g)")+ylab("Age (cal yr BP)")+theme_bw() + theme(axis.text.x=element_text(size=12),axis.title.x=element_text(size=12,face="bold"),axis.title.y = element_text(size=12,face="bold"))

phy_444


phy_445<-ggplot(phy_222, aes(y=Depth,(x=sqrt(phy_g_wet_sed))))+geom_point() +  scale_y_reverse(breaks = seq(0, 175, by = 10))  + ggtitle("")+xlab("Sqrt of Concentration (diat/g)")+ylab("Age (cal yr BP)")+theme_bw() + theme(axis.text.x=element_text(size=12),axis.title.x=element_text(size=12,face="bold"),axis.title.y = element_text(size=12,face="bold"))

phy_445


######Phytoliths just globular granulate
phy_4<-diat_merge%>%
      #select(Identifier,Type,Genus,Species2,Counts,Total_sediment_analysed_g,Number_of_transects)%>%
        filter(final_morphotype=='Globular granulate')%>% 
        group_by(Identifier)%>%
        mutate(Corrected_counts=Counts/Total_sediment_analysed_g)%>%
        mutate(countT= sum(Corrected_counts),countT2=sum(Counts)) %>%
        mutate(per=paste0(round(100*Corrected_counts/countT,2)))%>%
        mutate(glob_g_wet_sed = countT2/Total_sediment_analysed_g)%>%
        mutate(corr_trans= countT2/Number_of_transects)%>%
        filter(countT2 > 0)

phy_44<-left_join(phy_4,agedepth)
phy_443<-ggplot(phy_44, aes(x=phy_44$median,y=sqrt(glob_g_wet_sed)))+geom_point()

phy_443

phy_333 <- ggplot(phy_222, aes(x=phy_222$median,y=spi_g_wet_sed))+geom_point() 
phy_333


library(plotly)
##see ggplotly
#?ggplotly

#p2<-ggplotly(phy_443)
#print(p2)

p <- plot_ly(data = phy_222,x=~phy_222$median, y = ~Corrected_counts, color = ~final_morphotype)

print(p)


p2 <- plot_ly(data = phy_222,x=~phy_222$median, y = ~countT)

print(p2)

##RElative percentage (simple)
diat_c<-diatoms_counts %>%
        filter(Type=='Diatom')%>% 
            group_by(Identifier)%>%
        mutate(countT= sum(Counts)) %>%#Total counts of diatoms per depth
        mutate(per=paste0(round(100*Counts/countT,2)))%>%#percentage
        filter(countT > 0)%>%
        filter(Species2 != "Caloneis 999")
        ###not sure about this
#as.numeric(as.character(bulk3$Length.of.piece..cm.))

diat_all<-diatoms_counts %>%
        filter(Type=='Diatom')%>% 
            group_by(Identifier)%>%
        mutate(countT= sum(Counts)) %>%#Total counts of diatoms per depth
        mutate(per=paste0(round(100*Counts/countT,2)))#percentage
       # filter(countT > 30)%>%
        #filter(Species2 != "Caloneis 999")


##Put it in strat plot format?

diat_c2<- diat_c%>%
       spread(Species2, per) %>%
        select(Identifier,11:29)
        
##Maybe as a table for results

diat_c3<-gather(diat_c2,Species,Percentage,-Identifier)%>%
        filter(Percentage>0)%>%
        spread(Species,Percentage)

diat_c3[is.na(diat_c3)] <- 0


###Need to merge with new dates and model them with 0.5 cm resolution 


str(diat_c2)

#convert to Numeric
diat_c2[, c(1:20)] <- sapply(diat_c2[, c(1:20)], as.numeric)

#NAs to 0
diat_c2[is.na(diat_c2)] <- 0



correctdepths<-read.csv("C:/Users/Maria Jose Rivera/OneDrive - James Cook University/Australia renamed/Sanamere/Bulk density/replacement depths itrax_3.csv")

correctdepths<-correctdepths %>% rename(Depth=Real.depth)

diat_c5<-merge(diat_c2,correctdepths)


BAR <- Stratiplot(Identifier ~ . , data= diat_c3, type = c("h","g","l"), sort = "wa")

##with minimum relative abundance of 5 %
BAR2 <- Stratiplot(Identifier ~ . , data= chooseTaxa(diat_c2, max.abun = 5, n.occ = 1), xlab="Relative percentage (%)",
                   type = c("h","g"), sort = "var",na.rm = TRUE)
abline(h=c(90, 110), lty=1, col="red")


diat_c6<-select(diat_c5,-Identifier)

BAR3 <- Stratiplot(Depth ~ . , data= chooseTaxa(diat_c6, max.abun = 2, n.occ = 1), xlab="Relative percentage (%)",
                   type = c("h","g"), sort = "var",na.rm = TRUE)


?Stratiplot

age<-read.csv(here("data", "agedepth.csv"))
age$Identifier <- as.numeric(as.character(age$Identifier))

diatwithages<-left_join(diat_c2,age,by="Identifier")



##with ages

ages5<-read.table("C:/Users/Maria Jose Rivera/OneDrive - James Cook University/Australia renamed/Sanamere/Radiocarbon/Bacon_runs/SAN8_2019_4/SAN8_2019_4_35_ages.txt",skip=1)

colnames(ages5)<-c("Depth","max","min","median","mean")




diat_ages<-left_join(diat_c2,agedepth2)
diat_ages2<-select(diat_ages,-Identifier,-mean,-max,-min,-Depth)
diat_ages3<-filter(diat_ages2,median!="NA"& median<10000)
#diat_ages3<-filter(diat_ages2,median!="NA")
diat_ages4<-ungroup(diat_ages3)
diat_ages5<-select(diat_ages4,-Identifier)


BAR_age <- Stratiplot(median ~ . , data= chooseTaxa(diat_ages5, max.abun = 5, n.occ = 1), xlab="Relative percentage (%)",
                   type = c("h","g"), sort = "var",na.rm = TRUE,ylab="Age (cal yr BP)")


diat_ages33<-filter(diat_ages2,median!="NA")
#diat_ages3<-filter(diat_ages2,median!="NA")
diat_ages44<-ungroup(diat_ages33)
diat_ages55<-select(diat_ages44,-Identifier)

BAR_age2 <- Stratiplot(median ~ . , data= chooseTaxa(diat_ages55, max.abun = 5, n.occ = 1), xlab="Relative percentage (%)",
                   type = c("h","g"), sort = "var",na.rm = TRUE,ylab="Age (cal yr BP)")



############NOT SURE!


#pos1<-as.matrix(diat_c2$Identifier)
#posr1<-round(pos1, digits=1)
#final1<-"Surirella spiralis"
#l1<-match(final1,names(diat_c2))


diat_c4<- aggregate(x=diat_c2[,2:20], by=list(Identifier=diat_c2$Identifier), min, na.rm = TRUE)


d112<-as.matrix(diat_c4[,c(2:20)])

d1121<-diat_c4[,c(2:20)]

d1121[, c(1:19)] <- sapply(d1121[, c(1:19)], as.numeric)

Subs1 <- na.omit(d1121[])


d1121[is.na(d1121)] <- 0

d113<-as.matrix(d112[d112!=0]) 
d1131<-d112[d112!=0]
# matrix of XRF data excluding those beyond final

#d1s <- scale(d1, center=T, scale=T)
#standardised data

#pca <- prcomp(d1s, center=F, scale.=F)
#pca of the standardised data


dd<-diat_c2[,2:20]

dissim1<- vegdist(dd, method="bray")
#dissimilarity matrix computation
library(vegan)
library(rioja)
clust1 <- chclust(dissim1, method="coniss")
#constrained hierarchical clustering

# Ball and Stick
groups1<- bstick(clust1) #determine the appropriate number of significant clusters
ngroups1<- groups1$nGroups[which(groups1$dispersion <= groups1$bstick)]
ngroups1<- ngroups1[2]
cc1<- cutree(clust1, k = ngroups1)

# STRAT plot
#par(oma=c(2,1,1,1.2))
strat.plot(d1121, yvar=diat_c4$Identifier, clust=clust1, y.rev=TRUE, ylab="Depth (mm)", col.line="black", col.bar="black")
strat.plot(d1121, yvar=diat_c4$Identifier, clust=clust1, y.rev=TRUE, ylab="Depth (mm)", col.line="black", col.bar="black")

?strat.plot
?par
# check that strat plot is ok

x<-strat.plot(d1121, yvar=diat_c4$Identifier, clust=clust1, y.rev=TRUE, cex.axis=0.6, cex.yaxis=0.8, cex.ylabel=0.8, cex.lab=0.6, ylab="Depth (mm)",col.line="black", col.bar="black", las=3, mgp=c(3,1,0))

z<-as.matrix(1:ngroups1)

addClustZone(x, clust1, nZone=ngroups1, col=rainbow(length(z))[rank(z)])
c <- cutree(clust1, k=ngroups1)
diat_c4$clust1 <- c
  

###Concentration of diatoms
conc<-read.csv("C:/Users/Maria Jose Rivera/OneDrive - James Cook University/Australia renamed/Sanamere/Diatoms spicules/Concentration diatoms.csv")

diat_c_low<-diatoms_counts %>%
        filter(Type=='Diatom')%>% 
            group_by(Identifier)%>%
        mutate(countT= sum(Counts)) %>%#Total counts of diatoms per depth
        mutate(per=paste0(round(100*Counts/countT,2)))%>%#percentage
        filter(countT > 0)%>%
        filter(Species2 != "Caloneis 999")

conc2<-right_join(conc,diat_c_low,by="Identifier")%>%
         group_by(Identifier) %>%
   summarize(countss = mean(countT))
#con3<- aggregate(x=conc2[,2:20], by=list(Identifier=diat_c2$Identifier), min, na.rm = TRUE)
conc$Total_sediment_analysed_g<-as.numeric(as.character(conc$Total_sediment_analysed_g))
conc3<-left_join(conc2,conc)%>%
        mutate(diatpg=countss/Total_sediment_analysed_g)

conc4<-filter(conc3,Identifier>0.1)
conc5<-left_join(conc4,agedepth_final)

con_diat<-ggplot(conc5,aes(x=conc5$median,y=diatpg))+geom_point() + xlab("age")+ ylab("concentration")+ theme_bw()

print(con_diat)

str(agedepth_final$Identifier)

#######
spic_c<-diatoms_counts %>%
        filter(Type=="Spicule")%>% 
            group_by(Identifier)%>%
        mutate(countTsp= sum(Counts)) %>%
        mutate(per=paste0(round(100*Counts/countTsp,2)))%>%
        filter(countTsp > 0)

spic_c2<-right_join(conc,spic_c,by="Identifier")%>%
        mutate(sppg=countTsp/Total_sediment_analysed_g)


spic_c3<-left_join(spic_c2,agedepth)

con_spi<-ggplot(spic_c3,aes(x=median,y=sppg))+geom_point() + xlab("age")+ ylab("concentration")+ theme_bw()

print(con_spi)

plot(conc2$countss,conc2$Identifier)
diat_concgr<- ggplot(conc4, aes(x=diatpg,y=Identifier))+geom_point()+ scale_y_reverse() 
diat_concgr


spic_concgr<-ggplot(spic_c2, aes(x=sppg,y=Identifier))+geom_point()+ scale_y_reverse() 
spic_concgr


```
